---
title: "Analysis of Influence the Location of Starbucks "
author: "Jisun Lee, Huiyu Yi, Yuepeng Chen"
date: "12/5/2021"
output:
  html_document:
    fig_width: 8
    code_folding: hide
    highlight: tango
    toc: true
    toc_float:
      collapsed: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Dataset Details
The dataset was collected from the Kaggle website, and the data was created by the Starbucks store locator website. The data includes every Starbucks location in worldwide until November of 2021 with store numbers, country codes, ownership type code, operation time, latitude, longitude, address of the stores, and timezone of the stores' locations. Starbucks operates more than 28,000 retail stores in 49 countries.

# Objective 
Since Starbucks is one of the largest companies of coffee and beverage, it has spread throughout the world. So, through this project, we would like to compare the number of Starbucks by country to see which countries have a high number of Starbucks and to analyze the density of Starbucks by location. We are not only analyzing worldwide but also analyzing nationwide to see which states have the most number of Starbucks.   

```{r setup_data, include=FALSE}
library(plotly)
library(stats)
library(prob)
library(scales)
library(sampling)
library(wordcloud2)

data <- read.csv("https://raw.githubusercontent.com/CocoYi3327/cs544final/main/startbucks.csv")
Sys.setlocale('LC_ALL','C') # for encoding format

```

# Number and Density of Starbucks in World

```{r introdata}
fig <- data
fig <- fig %>%
  plot_ly(
    type = 'densitymapbox',
    lat = ~latitude,
    lon = ~longitude,
    coloraxis = 'coloraxis',
    radius = 10) 
fig <- fig %>%
  layout(
    mapbox = list(
      style="stamen-terrain",
      center= list(lon=180)), coloraxis = list(colorscale = "Viridis"))

fig

a <- sort(table(data$countryCode),decreasing = TRUE)
a <- as.data.frame(a)
fig1 <- plot_ly( a, x = a$Var1,y = a$Freq,type = 'bar')
fig1 <- fig1 %>% layout(title = "Number of Starbucks in Each Countries", yaxis = list(type = 'linear'))
fig1
```

# Summary of Stores Around the World
This data shows the summary of number of the stores around the world. There is a huge gap in average and median because there are some great numbers of the stores that having low density.

```{r summarize_world}
data1 <- table(data$countryCode)    #count the number of stores in each country
dataforsum <- as.data.frame(data1)
allsum <- summary(dataforsum$Freq)
paste("The",names(allsum), "number of Starbucks around the world is", allsum)
```

## Top 5 Countries of The Number of Starbucks Stores
These are the countries where have the most numbers of stores.

```{r top5stores}
top5 <- sort(data1,decreasing = TRUE)[1:5]
top5

fig3 <- plot_ly(y = dataforsum$Freq,type = 'box',name = "World")
fig3
```

Since the range of outliers is huge, we divided these data into 4 categories and use the smallest outlier as the boundary of "extremely high" class.

```{r summarize_world_outlier}
outliers <- boxplot.stats(dataforsum$Freq)$out   
Out <- which(dataforsum$Freq %in% c(outliers)) #position of outliers in the dataframe
min(dataforsum[Out,]$Freq)  
```

# Analyze By Categories

```{r Categorical_variables}
#set density as below:
# <= 375 low
# 375-675 moderate
# 675-975 high
# >= 975 extremely high

LtoM <- 375
MtoH <- 675
HtoE <- 975


#filter out each density
dataL <- as.data.frame(data1[data1<=LtoM])
dataM <- data1[data1>LtoM]
dataM <- as.data.frame(dataM[dataM<=MtoH])
dataH <- data1[data1>MtoH]
dataH <- as.data.frame(dataH[dataH<=HtoE])
dataE <- as.data.frame(data1[data1>HtoE])

#count each density
low <- nrow(dataL)
moderate <- nrow(dataM)
high <- nrow(dataH)
ehigh <- nrow(dataE)
#make the table to show number of each density
names(low) <- "number"
categorical <- rbind(low = low,moderate = moderate,high = high,Extremly_high = ehigh)
categorical <- data.frame(categorical)
categorical         #show the table
# plot out
x2 <- c("Low","Moderate","High","Extremely High")
fixedx2 <- factor(x2,levels = c("Low","Moderate","High","Extremely High"))
fig2 <- plot_ly(x = fixedx2 ,y = categorical$number,type = 'bar')
fig2 <- fig2 %>% layout(title = "Number of Countries in Each Level of Density")
fig2
```

## Summary of Low Density
Since the most countries are in low density, we only analyzed the low density.

```{r low_density}
lsum <- summary(dataL$Freq)
lsum
paste("The",names(lsum), "Number of Starbucks in Low Denisity Country is", lsum)
```

# Analyze the stores in the United States
Starbucks is founded in the United States, so United States has the most number of Starbucks. The following analysis is the analyzing of the stores in the United States.

```{r stores_US}
data2US <- subset(data,data$countryCode=="US")

#map of US

g <- list(
  scope = 'US',
  projection = list(type = 'albers usa'),
  showland = TRUE,
  landcolor = toRGB("gray95"),
  subunitcolor = toRGB("gray85"),
  countrycolor = toRGB("gray85"),
  countrywidth = 0.5,
  subunitwidth = 0.5
)

figMap <- plot_geo(data2US, lat = ~latitude, lon = ~longitude)
figMap <- figMap %>% add_markers(
  text = ~paste(streetAddressLine1, streetAddressLine2, streetAddressLine3, 
                paste("Ownership Type Code:", ownershipTypeCode), sep = "<br />"),
  color = ~ownershipTypeCode, symbol = I("square"), size = I(8), hoverinfo = "text"
)
figMap <- figMap %>% layout(
  title = 'Starbucks in US', geo = g
)
figMap
```

## Percentage of the stores in the United States

```{r US_percentage}
data2 <- table(data2US$countrySubdivisionCode)   #count the number of Starbucks in each state

data2_1 <- as.data.frame(data2)

figUSState <- plot_ly(data2_1, labels = ~Var1, values = ~Freq, type = 'pie')
figUSState <- figUSState %>% layout(title = 'Starbucks in US states',
            xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
            yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
figUSState
```

## Distribution of Data

```{r distribution}
size = nrow(data2US)
percentage = data2/size
percentage
```

### Probability For 20 US starbucks stores located in MA
We wondered what if we want to pick 20 stores from the United States, what the probability will be to get the store in Massachusetts.

```{r storesMA}
probMA <- percentage[names(percentage)=='MA']
probMA
pmfMA <- dbinom(1:20,size,probMA)
pmfMA
pmfMA1 <- as.data.frame(table(pmfMA))
pmfMA1$Freq <- c(1:20)
pmfMA1

plot(1:20,pmfMA,type="h",xlab = "20 times")   #pmf plot - each probability
```

### Probability For Picking One Store In Each States
```{r probEachState}
pmfUS <- dbinom(1,size,percentage)
pmfUS
```

## Sampling of Data
The data shows that there is a huge number of standard deviation. Also, randomized the data with normal distribution. 
```{r sampling}
mean <- mean(data2)
sd <- sd(data2)
mean
sd
#with a huge sd, what will the sampling show with US data
set.seed(9672)
# generate randomize 50 virtual states with normal distribution

normal_random <- rnorm(50, mean=mean,sd = sd);normal_random

hist(normal_random)
```

### Sample From Random
This data and graph present the samples with 4 different sample size that are 50, 100, 500 and 1000 from Starbucks in the United States. The pie charts show the significant differences between each states. 

```{r sampleRandom}
ssize <- c(50,100,500,1000)

#simple random sampling
for(size in ssize){
  s1 <- srswr(size,nrow(data2))
  pickedrow1 <- (1:nrow(data2))[s1!=0]
  pickedrow1 <- rep(pickedrow1,s1[s1!=0])
  simplesample1 <- data2US[pickedrow1, ]
  output <- table(simplesample1$countrySubdivisionCode);output
  output1 <- as.data.frame(table(output));output1
  output1$Freq<- c('CO','WA','NY');output1
  cat("The simple random sample lays out with sample size", size, "is\n", names(output), "\n", output, "\n")
  
}

#pie
s1 <- srswr(50,nrow(data2))
pickedrow1 <- (1:nrow(data2))[s1!=0]
pickedrow1 <- rep(pickedrow1,s1[s1!=0])
simplesample1 <- data2US[pickedrow1, ]
output <- table(simplesample1$countrySubdivisionCode)
output <- as.data.frame(output)
figRandomSampling50 <- plot_ly(output, labels = ~Var1, values = ~Freq, type = 'pie')
figRandomSampling50 <- figRandomSampling50 %>% layout(title = 'Simple Random Sampling with Sample Size = 50', xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                  yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
figRandomSampling50

s1 <- srswr(100,nrow(data2))
pickedrow1 <- (1:nrow(data2))[s1!=0]
pickedrow1 <- rep(pickedrow1,s1[s1!=0])
simplesample1 <- data2US[pickedrow1, ]
output <- table(simplesample1$countrySubdivisionCode)
output <- as.data.frame(output)
figRandomSampling100 <- plot_ly(output, labels = ~Var1, values = ~Freq, type = 'pie')
figRandomSampling100 <- figRandomSampling100 %>% layout(title = 'Simple Random Sampling with Sample Size = 100', xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                    yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
figRandomSampling100

s1 <- srswr(500,nrow(data2))
pickedrow1 <- (1:nrow(data2))[s1!=0]
pickedrow1 <- rep(pickedrow1,s1[s1!=0])
simplesample1 <- data2US[pickedrow1, ]
output <- table(simplesample1$countrySubdivisionCode)
output <- as.data.frame(output)
figRandomSampling500 <- plot_ly(output, labels = ~Var1, values = ~Freq, type = 'pie')
figRandomSampling500 <- figRandomSampling500 %>% layout(title = 'Simple Random Sampling with Sample Size = 500', xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                    yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
figRandomSampling500

s1 <- srswr(1000,nrow(data2))
pickedrow1 <- (1:nrow(data2))[s1!=0]
pickedrow1 <- rep(pickedrow1,s1[s1!=0])
simplesample1 <- data2US[pickedrow1, ]
output <- table(simplesample1$countrySubdivisionCode)
output <- as.data.frame(output)
figRandomSampling1000 <- plot_ly(output, labels = ~Var1, values = ~Freq, type = 'pie')
figRandomSampling1000 <- figRandomSampling1000 %>% layout(title = 'Simple Random Sampling with Sample Size = 1000', xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                     yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
figRandomSampling1000
```

## Systematic Sampling

```{r systematic_sampling}
for(size in ssize){
  N <- nrow(data2)
  k <- ceiling(N/size)
  r <- sample(k,1)
  s <- seq(r,by=k,length = size)
  systematicsample <- data2US[s, ]
  output <- table(systematicsample$countrySubdivisionCode)
  cat("The systematic sample layout with sample size", size, "is\n", names(output), "\n", output, "\n")
}

#pie
N <- nrow(data2)
k <- ceiling(N/50)
r <- sample(k,1)
s <- seq(r,by=k,length = 50)
systematicsample <- data2US[s, ]
output <- table(systematicsample$countrySubdivisionCode);output
output <- as.data.frame(output);output
figSystematicSampling50 <- plot_ly(output, labels = ~Var1, values = ~Freq, type = 'pie')
figSystematicSampling50 <- figSystematicSampling50 %>% layout(title = 'Systematic Sampling with Sample Size = 50', xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                  yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
figSystematicSampling50

N <- nrow(data2)
k <- ceiling(N/100)
r <- sample(k,1)
s <- seq(r,by=k,length = 100)
systematicsample <- data2US[s, ]
output <- table(systematicsample$countrySubdivisionCode);output
output <- as.data.frame(output);output
figSystematicSampling100 <- plot_ly(output, labels = ~Var1, values = ~Freq, type = 'pie')
figSystematicSampling100 <- figSystematicSampling100 %>% layout(title = 'Systematic Sampling with Sample Size = 100', xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE), yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
figSystematicSampling100

N <- nrow(data2)
k <- ceiling(N/500)
r <- sample(k,1)
s <- seq(r,by=k,length = 500)
systematicsample <- data2US[s, ]
output <- table(systematicsample$countrySubdivisionCode);output
output <- as.data.frame(output);output
figSystematicSampling500 <- plot_ly(output, labels = ~Var1, values = ~Freq, type = 'pie')
figSystematicSampling500 <- figSystematicSampling500 %>% layout(title = 'Systematic Sampling with Sample Size = 500', xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE), yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
figSystematicSampling500

N <- nrow(data2)
k <- ceiling(N/1000)
r <- sample(k,1)
s <- seq(r,by=k,length = 1000)
systematicsample <- data2US[s, ]
output <- table(systematicsample$countrySubdivisionCode);output
output <- as.data.frame(output);output
figSystematicSampling1000 <- plot_ly(output, labels = ~Var1, values = ~Freq, type = 'pie')
figSystematicSampling1000 <- figSystematicSampling1000 %>% layout(title = 'Systematic Sampling with Sample Size = 1000', xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE), yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
figSystematicSampling1000

```

# Conclusion
Throughout the analysis, we were focused on the number of locations of Starbucks in the world and the United States. Before we started analyzing the data, we expected a high volume of Starbucks in Washington since Starbucks started from Washington state. Also, we assume that one of the European countries could be the top five countries with a large number of Starbucks stores because most western people start their days with coffee. However, worldwide, it was quite surprising that Starbucks is very popular in East Asia especially in China, South Korea, and Japan. Nationwide, although Washington is the founder state of Starbucks, California has the most number of Starbucks stores in the United States.

```{r wordcloud}
wordclouddata <- as.data.frame(table(data2US$countrySubdivisionCode))
wordcloud2(wordclouddata)
```
